---
title             : "Supplement: National Longitudinal Evidence for Growth in Subjective Wellbeing from Spiritual Beliefs"
shorttitle        : "Title"
author: 
  - name          : "Ben Highland"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # First author
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & editing
  - name          : "Joseph Bulbulia"
    affiliation   : "1,2"
    role:
      - Writing - 
      - Analysis 
affiliation:
  - id            : "1"
    institution   : "Wake Forest Med School "
  - id            : "2"
    institution   : "Victoria University"
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
 Previous research finds an association between spirituality and subjective well-being. However, the widespread use of tautological spirituality scales, poorly defined concepts of spirituality, and heavy reliance on cross-sectional samples cast doubts. Here, we leverage nine waves of panel data from a nationally diverse longitudinal study to systematically test whether having spiritual beliefs leads to growth in personal well-being and life satisfaction ($N$ = 20979, New Zealand, 2010-2018). Contrary to previous research, we find that belief in a spirit or life force predicts lower personal well-being and life-satisfaction. However, in support of previous speculation, beliefs in a spirit or life force predict increasing personal well-being and life satisfaction over time relative to disbelief. These finding are robust after to known demographic influences, and intriguingly, hold among those who believe in a God but disbelieve in a Spirit or Life Force. The recent growth in spiritual beliefs and decline in traditional religion across many industrial societies motivates further causal investigations of the mechanisms by which spiritual beliefs lead to growth in subjective well-being. 
  
  
  <!-- https://tinyurl.com/ybremelq -->
keywords          : "keywords"
wordcount         : "X"
bibliography      : ["b-references.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : "html_document" 
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```
```{r global_options, echo=FALSE, include = FALSE}
knitr::opts_chunk$set(fig.path="Figs/", 
                      message=FALSE, 
                      warning=FALSE,
                      collapse =TRUE,
                      echo=TRUE, 
                      #results="hide", 
                      fig.width= 10,
                      fig.height=8,
                      tidy = "styler")
```
```{r load_libraries, echo=FALSE, include=FALSE}
source("libs.R")
source("funs.R")
```
```{r, sessioninfo, include=FALSE}
#  custom function for citing packages. 
cite_packages()

# custom function for my machine to read data. you'll need to read data to your machine. tweak function in the `funs.R' script for your machine
d<-data_read_mymachine()

# function to clean data, specify number of waves as 3 
d_3<-data_clean_spirit_wellbeing(d,3) # d = dataframe, 3 = number of waves
# function to count uinque ides
show_unique_id(d_3$Id) 

# function to count waves for participants
count_waves_participants(d_3)

# table of beliefs 
table(d_3$Beliefs)

# years
range(d_3$years)
```

```{r}
# must remove Furniture package before running table 1
demographic_table(d_3)
```

```{r}
beliefs_table(d_3)
```

```{r latex_data_table}
# you might need to install the dev verion.//remotes::install_github("tysonstanley/furniture")
demographic_table_latex(d_3)
```

# Bayesian estimation

```{r}
forumula_bayesPWI <- bf(PWI ~  1 +  years * Beliefs + (1|Id))
forumula_bayesLIFESAT <- bf(PWI ~  1 +  years * Beliefs + (1|Id))

# PWI
mod.1aaB <-brm(forumula_bayesPWI, data= d_3, file ="mod.1aaB")

# LIFE SAT
mod.2aaB <-brm (forumula_bayesLIFESAT, data= d_3,data= dfben,
                file ="mod.2aaB")
```



```{r bayesian_pwi}
conditional_effects(mod.1aaB)[[3]]
```
```{r bayesian_lifesat}
conditional_effects(mod.2aaB)[[3]]

```

parameters::check_heterogeneity(mod02, group = "ID")

# inference holds, but can we use this method with factors? What do the contrasts mean? 
tab_model(mod01)
tab_model


## BAYES



```{r bayesian_pwi_plot }
pr.LS_b <- ggpredict(model = mod.2aaB, terms = c("years [0:9]","Beliefs"), 
                    ci.lvl = 0.95,
                    type = "fe",
                    typical = "mean",
                   # condition = c(Euro =1),
                    back.transform = TRUE,
                    ppd = FALSE,
                    interval = "confidence")
p1<-plot(pr.LS_b, facets = T) + 
 # scale_y_continuous(limits=c(4.75,5.25) )  + 
  gghighlight()  +  theme_blank()+ 
  ggtitle("Bayesian Model Predicted Values of Personal Wellbeing") 
p1
pr.LS_b
```
```



```{r lme model}
# Inference holds 
library(lme4)
mod.1 <-lmer (PWI ~  1 +  Years * Beliefs +  Age.10yrs.C + Deprivation.S + Edu.S  + Employed + EthnicCats + Male  + Partner  + Pol.Orient.S + Urban + (1|Id), data= dfben, na.action = na.omit)
mod.2 <-lmer (LIFESAT ~ 1 + Years * Beliefs+ Age.10yrs.C + Deprivation.S + Edu.S  + Employed + EthnicCats + Male  + Partner  + Pol.Orient.S + Urban + (1|Id), data= dfben, na.action = na.omit)
summary(mod.1)
summary(mod.2)


## Try models with generation as rand effect. Reason: how to interpret differences in intercepts?  # USING glmmTMB because lmer is crashing SAME RESULT SO IGNORE
# mod.1 <-glmmTMB(LIFESAT ~ Years * Beliefs + Deprivation.S + Edu.S  + Employed + EthnicCats + Male  + Partner  + Pol.Orient.S + Urban + (1|Id) + (1|GenCohort), data= dfben)
# 
# mod.2 <-glmmTMB(PWI ~ Years * Beliefs + Deprivation.S + Edu.S  + Employed + EthnicCats + Male  + Partner  + Pol.Orient.S + Urban + (1|Id) + (1|GenCohort), data= dfben)
```

```{r check collinearity}
# Note High VIFS from 
performance::check_collinearity(mod.1)
performance::check_collinearity(mod.2)
```

VIF high,  this is the years x factor interaction. See if it makes a difference by centering years.

```{r model centering years}
library(lme4)
mod.1a <-lmer (PWI ~  1 +  yearsC * Beliefs +  Age.10yrs.C + Deprivation.S + Edu.S  + Employed + EthnicCats + Male  + Partner  + Pol.Orient.S + Urban + (1|Id), data= dfben)
mod.2a <-lmer (LIFESAT ~ 1 + yearsC * Beliefs+ Age.10yrs.C + Deprivation.S + Edu.S  + Employed + EthnicCats + Male  + Partner  + Pol.Orient.S + Urban + (1|Id), data= dfben)
summary(mod.1a)
summary(mod.2a)
# identical result
performance::check_collinearity(mod.1a)
performance::check_collinearity(mod.2a)
```

Check reviewers interest in correlation of deprivation and having a partner.
```{r}
m<-lmer (NZdep ~ Partner + (1|Id), data= dfben, na.action = na.omit)
tab_model(m)
model_parameters(m)
```




Check whether model is robust without control covariates

```{r robust to years and beliefs only}
library(lme4)
mod.1aa <-lmer (PWI ~  1 +  yearsC * Beliefs + (1|Id), data= dfben)
mod.2aa <-lmer (LIFESAT ~ 1 + yearsC * Beliefs + (1|Id), data= dfben)
)
# identical result
sjPlot::tab_model(mod.1aa,mod.2aa)
```

```{r check collinearity}
# Note High VIFS from 
performance::check_collinearity(mod.1aa)
performance::check_collinearity(mod.2aa)

parameters::check_heterogeneity(mod.1aa, group = "ID")
parameters::check_heterogeneity(mod.2aa, group = "ID")

```
Indeed, models are robust without control covariates
```{r cache = TRUE, dependson="mod.2", dependson="mod.1"}
tab_model(mod.2, mod.1) # Table
```

Try with a tensor spline

```{r}
# complete cases
dfbenTS<-dfben%>%
  select(PWI,LIFESAT,yearsC,Beliefs,Id)%>%
  filter(complete.cases(.))
```


```{r}
# check model with bayesian estimator (preferred)
mod.1aaB_ts <-brm(PWI ~  1 +  ts(years) + (1|Id), data= dfbenTS, file ="mod.1aaB_ts")

mod.2aaB_ts <-brm (LIFESAT ~ 1 + ts(Beliefs,years) + (1|Id), data= dfbenTS,
                file ="mod.2aaB_ts")
```


```{r}
str(dfben$Beliefs)
conditional_effects(mod.1aaB_ts, surface = TRUE)
conditional_smooths(mod.1aaB_ts)
```

```{r}
conditional_effects(mod.2aaB_ts, surface = TRUE)
```



```{r bayesian_pwi_plot }
pr.PWI_b <- ggpredict(model = mod.1aaB, terms = c("years [0:9]","Beliefs"), 
                    ci.lvl = 0.95,
                    type = "fe",
                    typical = "mean",
                   # condition = c(Euro =1),
                    back.transform = TRUE,
                    ppd = FALSE,
                    interval = "confidence")
p1<-plot(pr.PWI_b, facets = T) + 
 # scale_y_continuous(limits=c(4.75,5.25) )  + 
  gghighlight()  +  theme_blank()+ 
  ggtitle("Bayesian Model Predicted Values of Personal Wellbeing") 
p1
pr.PWI_b
```

```{r bayesian_pwi_plot }
pr.LS_b <- ggpredict(model = mod.2aaB, terms = c("years [0:9]","Beliefs"), 
                    ci.lvl = 0.95,
                    type = "fe",
                    typical = "mean",
                   # condition = c(Euro =1),
                    back.transform = TRUE,
                    ppd = FALSE,
                    interval = "confidence")
p1<-plot(pr.LS_b, facets = T) + 
 # scale_y_continuous(limits=c(4.75,5.25) )  + 
  gghighlight()  +  theme_blank()+ 
  ggtitle("Bayesian Model Predicted Values of Personal Wellbeing") 
p1
pr.LS_b
```


```{r bayesian_pwi_plot }
pr.PWI_b <- ggpredict(model = mod.21aaB, terms = c("years [0:9]","Beliefs"), 
                    ci.lvl = 0.95,
                    type = "fe",
                    typical = "mean",
                   # condition = c(Euro =1),
                    back.transform = TRUE,
                    ppd = FALSE,
                    interval = "confidence")
p1<-plot(pr.PWI_b, facets = T) + 
 # scale_y_continuous(limits=c(4.75,5.25) )  + 
  gghighlight()  +  theme_blank()+ 
  ggtitle("Vayesian Model Predicted Values of Personal Wellbeing") 
p1
pr.PWI_b
```



```{r bayesian_pwi_plot }
pr.LS_b <- ggpredict(model = mod.2aaB, terms = c("years [0:9]","Beliefs"), 
                    ci.lvl = 0.95,
                    type = "fe",
                    typical = "mean",
                   # condition = c(Euro =1),
                    back.transform = TRUE,
                    ppd = FALSE,
                    interval = "confidence")
p1<-plot(pr.LS_b, facets = T) + 
 # scale_y_continuous(limits=c(4.75,5.25) )  + 
  gghighlight()  +  theme_blank()+ 
  ggtitle("Bayesian Model Predicted Values of Personal Wellbeing") 
p1
pr.LS_b
```







```{r, echo = FALSE, include=FALSE}
te00 <-texreg::extract(
  mod.1,
  level = 0.95,
  include.random = TRUE,
  include.rsquared = T,
  include.nobs = T,
  include.loo.ic = T,
  include.waic = F)

texreg(list(te00),
                custom.model.names = c("PWI"),
                caption = "Personal Wellbeing",
                sideways = F,
                scalebox = .5,
                #fontsize= "footnotesize",
                label = "tab:REGRESS_1",
                ci.force.level = 0.95, bold = 0.05,
                settingstars = 0,
                booktabs = TRUE,
                custom.note ="")
```



```{r, echo = FALSE, include=FALSE}
te02 <-texreg::extract(
  mod.2,
  level = 0.95,
  include.random = TRUE,
  include.rsquared = T,
  include.nobs = T,
  include.loo.ic = T,
  include.waic = F)

texreg(list(te02),
                custom.model.names = c("PWI"),
                caption = "LifeSatisfaction",
                sideways = F,
                scalebox = .5,
                #fontsize= "footnotesize",
                label = "tab:REGRESS_1",
                ci.force.level = 0.95, bold = 0.05,
                settingstars = 0,
                booktabs = TRUE,
                custom.note ="")
texreg(list(te02),
                custom.model.names = c("PWI"),
                caption = "LifeSatisfaction",
                sideways = F,
                scalebox = .5,
                #fontsize= "footnotesize",
                label = "tab:REGRESS_1",
                ci.force.level = 0.95, bold = 0.05,
                settingstars = 0,
                booktabs = TRUE,
                custom.note ="")

texreg(list(te00, te02), dcolumn = F, booktabs = TRUE, scalebox = .6,ci.force.level = 0.95, bold = 0.05,
                settingstars = 0, caption = "Regression Models")
```

```{r, echo = FALSE, include=FALSE}
te00 <-texreg::extract(
  mod.1,
  level = 0.95,
  include.random = TRUE,
  include.rsquared = T,
  include.nobs = T,
  include.loo.ic = T,
  include.waic = F)
texreg(list(te00),
                custom.model.names = c("PWI"),
                caption = "Personal Wellbeing",
                sideways = F,
                scalebox = .5,
                #fontsize= "footnotesize",
                label = "tab:REGRESS_1",
                ci.force.level = 0.95, bold = 0.05,
                settingstars = 0,
                booktabs = TRUE,
                custom.note ="")
```

Plot models
```{r USEcoefficientplots}
plot_models(mod.2, mod.1) + ylim(-.4, .75) + theme_abyss() + scale_colour_brewer(labels = c("Personal Wellbeing", "Life Satisfaction")) # Plots
```
```{r}
library(parameters)
g1<-plot(parameters::model_parameters(mod.1))+ ggtitle("Personal Wellbeing Coefficients")
g2<-plot(parameters::model_parameters(mod.2))+ ggtitle("Life Satisfaction Coefficients")
```

```{r USE_2_coefficientplots}
g1/g2
range(dfben$yearsC)
```


```{r cache = TRUE, dependson = "mod.1"}
#### Predicted Effects ####
pr.PWI <- ggpredict(model = mod.1, terms = c("Years [0:9]","Beliefs"), 
                    ci.lvl = 0.95,
                    type = "fe",
                    typical = "mean",
                   # condition = c(Euro =1),
                    back.transform = TRUE,
                    ppd = FALSE,
                    interval = "confidence")
p1<-plot(pr.PWI, facets = T) + 
 # scale_y_continuous(limits=c(4.75,5.25) )  + 
  gghighlight()  +  theme_blank()+ 
  ggtitle("Predicted Values of Personal Wellbeing") 
p1
pr.PWI
```
```{r pwi_expected}
```

```{r predictlifesat}
pr.LIFESAT <- ggpredict(model = mod.2, terms = c("Years [0:9]", "Beliefs"),
                        ci.lvl = 0.95,
                        type = "fe",
                        typical = "mean",
                     #   condition = c(Euro =1),
                        back.transform = TRUE,
                        ppd = FALSE,
                        interval = "confidence")
# print expected intervals for the y-hats reported in the conclusion
pr.LIFESAT

p2<-plot(pr.LIFESAT,facets = T) + 
 # scale_y_continuous(limits=c(6.35,6.85) ) + 
  gghighlight() + theme_blank() + 
  ggtitle("Predicted Values of Life Satisfaction") #+   scale_colour_brewer(palette = "Zissou1")
p2
```

## Reporting

### equations
Life satisfaction Model 1 equation

<!-- ```{r eq1} -->
<!-- library(equatiomatic) -->
<!-- print(extract_eq(mod.1, wrap = TRUE,terms_per_line =3)) -->
<!-- ``` -->

<!-- PWI Model 2 equation -->
<!-- ```{r eq2} -->
<!-- library(equatiomatic) -->
<!-- print(extract_eq(mod.2, wrap = TRUE, use_coefs=TRUE,terms_per_line = 3)) -->
<!-- ``` -->


<!-- ## report -->

<!-- ### Model 1 -->
<!-- model 1 report: for publication change all "significants" to "reliable" -->

<!-- short report: -->
<!-- ```{r, report1, cache =TRUE, dependson=mod.1,include=FALSE} -->
<!-- easystats::model_text(mod.1) -->
<!-- ``` -->

<!-- short report -->
<!-- ```{r, cache=TRUE, include=FALSE } -->
<!-- library(report) -->
<!-- r1<- easystats::report(mod.1) -->
<!-- easystats::table_short(r1) -->
<!-- easystats::text_short(r1) -->
<!-- ``` -->


<!-- ```{r, cache =TRUE, dependson=mod.1, include=FALSE} -->
<!-- r1<- easystats::report(mod.1) -->
<!-- easystats::text_long(r1) -->
<!-- ``` -->
<!-- short report -->
<!-- ```{r, cache =TRUE, dependson=mod.2,include=FALSE} -->
<!-- # Model 2 -->
<!-- # For publication change all "significants" to "reliable" -->

<!-- easystats::model_text(mod.2) -->
<!-- ``` -->

<!-- short report -->
<!-- ```{r,include=FALSE} -->
<!-- r2 <- easystats::report(mod.2) -->
<!-- easystats::text_short(r2) -->
<!-- easystats::table_short(r2) -->
<!-- ``` -->

<!-- long report -->
<!-- ```{r,include=FALSE} -->
<!-- r2<- easystats::report(mod.2) -->
<!-- easystats::text_long(r2) -->
<!-- ``` -->



Graphs of predictions.

```{r USEPWI_expected}
p1 #+ plot_annotation(title = 'All cases Plot')
```

```{r USElifsat_expected}
p2 #+ plot_annotation(title = 'All cases Plot')
```




## Imputed Analysis


```{r echo = TRUE,  cache = TRUE, dependson = "dfben"}
# Imputed data
prp<- dfben %>% # Remove what we do not need anymore
  dplyr::select(c(Beliefs, Age, Id, Education, NZdep,KESSLER6,LIFESAT,PWI,Pol.Orient,Relid,EthnicCats,Partner,Employed,Male,Urban,Years,Wave))

# total ids = 21,705
length(unique(prp$Id))


#Make dataframes
prp<-as.data.frame(prp)

#Bifurcated imputation - This is presented in the main text
set.seed(1234)
imputed <- amelia(
  prp, #dataset to impute
  m = 10, # number of imputations
  cs= c("Id"),
  ts= c("Years"),
  noms = c("EthnicCats",
           "Urban",
           "Partner",
           "Male",
           "Employed",
           "Beliefs"),
  idvars=c("Wave","PWI","LIFESAT"), # not imputing outcomes
  polytime = 3) #https://stackoverflow.com/questions/56218702/missing-data-warning-r
#saveRDS(imputed,"imputed")
#imputed<- readRDS("imputed")
```
```{r}

# center and scale indiators
imputed.2 <- transform.amelia(imputed,
                              Age.10yrs = (Age/10),
                              yearsC = scale(Years, center=TRUE,scale=FALSE),
                              Pol.Orient.S =scale(Pol.Orient, center=TRUE,scale=TRUE),
                              Employed = factor(Employed),
                              Ethnicity = as.factor(EthnicCats),
                              Urban = factor(Urban),
                              Deprivation.S = scale(NZdep, scale=TRUE, center=TRUE),
                              Edu.S = scale(Education, scale =TRUE,center=TRUE),
                              Male = as.factor(Male),
                              PWI = as.numeric(PWI),
                              LIFESAT = as.numeric(LIFESAT),
                              Beliefs = as.factor(Beliefs),
                              Id =as.factor(Id))
# center an d scale age
imputed3 <- transform.amelia(imputed.2,
                                     Age.10yrs.C = scale(Age.10yrs,scale =FALSE, center=TRUE))
```


```{r cache = TRUE}
# run models iterating over imputed data
m <- 10
models3 <- NULL
for(i in 1:m) {
  models3[[i]] <- lmer(PWI ~ Years * Beliefs + Age.10yrs.C + Deprivation.S + Edu.S  + Employed + EthnicCats + Male  + Partner  + Pol.Orient.S + Urban + (1|Id), data=imputed3$imputations[[i]])
}
```

```{r, cache=TRUE, dependson= models3}
#devtools::install_github("easystats/parameters") Get development version
library(parameters)
mps3 <- lapply(models3, model_parameters)
parameters::pool_parameters(mps3)
mp3<-pool_parameters(mps3)
```


```{r coef_PWI_imputed}
# coeff plot
plot(mp3) + ggtitle("Personal Wellbeing Coefficients (Imputed)") # pick your  own title
```

```{r cache = TRUE, dependson = models3}
## expectation
m<-10
out<-NULL
for(i in 1:m) {
  out[[i]] <- ggpredict(models3[[i]], terms =c("Years [0:9]","Beliefs"))
}

m<-10
plots<-NULL
for(i in 1:m) {
  plots[[i]] <- plot(out[[i]], facets = T)# + scale_y_continuous(limits=c(6.35,6.85) )
}
```
```{r, echo=FALSE}
# Inspect all  # No differences
# plots[[1]]
# plots[[2]]
# plots[[3]]
# plots[[4]]
# plots[[5]]
# plots[[6]]
# plots[[7]]
# plots[[8]]
# plots[[9]]
# plots[[10]]
```
```{r predicted_PWI_impute}
# to highlight differencs
explectationGraphPWI <-plots[[10]] + gghighlight() + ggtitle("Predicted Values of Personal Wellbeing (imputed)")
explectationGraphPWI
```
```{r cache =TRUE}
## life sat models
m <- 10
modelsL3 <- NULL

for(i in 1:m) {
  modelsL3[[i]] <- lmer(LIFESAT ~ Years * Beliefs + Age.10yrs.C + Deprivation.S + Edu.S  + Employed + EthnicCats + Male  + Partner  + Pol.Orient.S + Urban +  (1|Id), data=imputed3$imputations[[i]])
}
```
```{r, cache =TRUE, dependson =  modelsL3}
mpl3 <- lapply(modelsL3, model_parameters)
parameters::pool_parameters(mpl3)
ml3<-pool_parameters(mpl3)
ml3 # table
p13<-plot(ml3)

p13<- p13 +  labs(title ="Coefficients Life Satisafaction (imputed)")
# get estimates for PWI from above
p23 <- plot(mp3) + labs(title ="Coefficients Personal Wellbeing (imputed)")
```

```{r coefficient_plot_both_imputed}
 p23/p13 +  plot_annotation(tag_levels = 'i')
```

```{r, cache =TRUE, dependson = "modelsL3"}
# Expectation plots
m<-10
out2<-NULL
for(i in 1:m) {
  out2[[i]] <- ggpredict(modelsL3[[i]], terms = c("Years [0:9]", "Beliefs"),
                         ci.lvl = 0.95,
                         type = "fe",
                         typical = "mean",
                         #   condition = c(Euro =1),
                         back.transform = TRUE,
                         ppd = FALSE,
                         interval = "confidence")
}

m<-10
plots2<-NULL
for(i in 1:m) {
  plots2[[i]] <- plot(out2[[i]], facets = T) #+ scale_y_continuous(limits=c(4.75,5.25) )
}
```
```{r echo = FALSE}
# Inspect all  # No differences
# plots2[[1]]
# plots2[[2]]
# plots2[[3]]
# plots2[[4]]
# plots2[[5]]
# plots2[[6]]
# plots2[[7]]
# plots2[[8]]
# plots2[[9]]
# plots2[[10]]

library(gghighlight)

# Just using one graph
explectationGraphLS <-plots2[[10]] + gghighlight() + ggtitle("Predicted Values of Life Satisfaction (imputed)")
```


```{r predicted_lifesat_imputed, cache=TRUE}
explectationGraphLS
```
```{r combograph_imputed}
# Combo_Graph
#explectationGraphPWI/explectationGraphLS + plot_annotation(title = "Imputed DataSet")
##
```

## analysis with centred time (to avoid multicollinearity)

```{r cache = FALSE}
# run models iterating over imputed data
m <- 10
models33 <- NULL
for(i in 1:m) {
  models33[[i]] <- lmer(PWI ~ yearsC * Beliefs + Age.10yrs.C + Deprivation.S + Edu.S  + Employed + EthnicCats + Male  + Partner  + Pol.Orient.S + Urban + (1|Id), data=imputed3$imputations[[i]])
}
```

```{r, cache=FALSE, dependson= models33}
#devtools::install_github("easystats/parameters") Get development version
library(parameters)
mps33 <- lapply(models33, model_parameters)
parameters::pool_parameters(mps33)
mp33<-pool_parameters(mps33)

```


```{r coef_PWI_imputed_C}
# coeff plot
plot(mp33) + ggtitle("Personal Wellbeing Coefficients (Imputed)") # pick your  own title
```

```{r cache = FALSE, dependson = models3}
## expectation
m<-10
out<-NULL
for(i in 1:m) {
  out[[i]] <- ggpredict(models33[[i]], terms =c("yearsC [minmax]","Beliefs"))
}

m<-10
plots<-NULL
for(i in 1:m) {
  plots[[i]] <- plot(out[[i]], facets = T)# + scale_y_continuous(limits=c(6.35,6.85) )
}
```
```{r, echo=FALSE}
# Inspect all  # No differences
# plots[[1]]
# plots[[2]]
# plots[[3]]
# plots[[4]]
# plots[[5]]
# plots[[6]]
# plots[[7]]
# plots[[8]]
# plots[[9]]
# plots[[10]]
```
```{r predicted_PWI_impute_C}
# to highlight differencs
explectationGraphPWI_C <-plots[[10]] + gghighlight() + ggtitle("Predicted Values of Personal Wellbeing (imputed)")
explectationGraphPWI_C
```
```{r cache =TRUE}
## life sat models
m <- 10
modelsL33 <- NULL

for(i in 1:m) {
  modelsL33[[i]] <- lmer(LIFESAT ~ yearsC * Beliefs + Age.10yrs.C + Deprivation.S + Edu.S  + Employed + EthnicCats + Male  + Partner  + Pol.Orient.S + Urban +  (1|Id), data=imputed3$imputations[[i]])
}
```
```{r, cache =FALSE, dependson =  modelsL33}
mpl33 <- lapply(modelsL33, model_parameters)
parameters::pool_parameters(modelsL33)
ml33<-pool_parameters(mpl33)
ml33 # table
p133<-plot(ml33)

p133<- p133 +  labs(title ="Coefficients Life Satisafaction (imputed)")
# get estimates for PWI from above
p233 <- plot(ml33) + labs(title ="Coefficients Personal Wellbeing (imputed)")
```

```{r coefficient_plot_both_imputed_C}
 p233/p133 +  plot_annotation(tag_levels = 'i')
```

```{r, cache =FALSE, dependson = "modelsL3"}
# Expectation plots
m<-10
out2<-NULL
for(i in 1:m) {
  out2[[i]] <- ggpredict(modelsL33[[i]], terms = c("yearsC [minmax]", "Beliefs"),
                         ci.lvl = 0.95,
                         type = "fe",
                         typical = "mean",
                         #   condition = c(Euro =1),
                         back.transform = TRUE,
                         ppd = FALSE,
                         interval = "confidence")
}

m<-10
plots2<-NULL
for(i in 1:m) {
  plots2[[i]] <- plot(out2[[i]], facets = T) #+ scale_y_continuous(limits=c(4.75,5.25) )
}
```
```{r echo = FALSE}
# Inspect all  # No differences
# plots2[[1]]
# plots2[[2]]
# plots2[[3]]
# plots2[[4]]
# plots2[[5]]
# plots2[[6]]
# plots2[[7]]
# plots2[[8]]
# plots2[[9]]
# plots2[[10]]

library(gghighlight)
```

```{r explectationGraphLS_C}
# Just using one graph
explectationGraphLS_C <-plots2[[10]] + gghighlight() + ggtitle("Predicted Values of Life Satisfaction (imputed)")
explectationGraphLS_C
```





<!-- We might want to look at within/between indivual change (i.e. do people who change in degree of spirit beliefs manifest different wellbeing.  I ran this as below, however, what we really want is a markov model, where we compare state changes between the different types of belief. So this model is not useful. For more on demeaning see:  -->
<!-- https://easystats.github.io/parameters/articles/demean.html -->

<!-- ```{r} -->
<!-- dfben <- cbind( -->
<!--   dfben, -->
<!--   parameters::demean(dfben, select = c("Beliefs"), group = "Id") -->
<!-- ) -->
<!-- ``` -->
<!-- ```{r models, cache = TRUE, dependson = "dfben"} -->
<!-- ### Spirit Belief Models ###  -->
<!-- mod01<-lmer (PWI ~ Years + -->
<!--                 Beliefs__Skeptic__between  +   -->
<!--                 Beliefs__SpiritExcludesGod__between +  -->
<!--                 Beliefs_GodAndSpirit_between  +  -->
<!--                 Beliefs_GodExcludesSpirit_between + -->
<!--                 Beliefs__Skeptic__within  +   -->
<!--                 Beliefs__SpiritExcludesGod__within +  -->
<!--                 Beliefs_GodAndSpirit_within  +  -->
<!--                 Beliefs_GodExcludesSpirit_within + -->
<!--                 (1|Id), data= dfben, na.action = na.omit) -->

<!-- parameters::check_heterogeneity(mod01, group = "ID") -->
<!-- parameters::check_heterogeneity(mod01, group = "ID") -->

<!-- mod02<-lmer (LIFESAT ~ Years + -->
<!--                 Beliefs__Skeptic__between  +   -->
<!--                 Beliefs__SpiritExcludesGod__between +  -->
<!--                 Beliefs_GodAndSpirit_between  +  -->
<!--                 Beliefs_GodExcludesSpirit_between + -->
<!--                 Beliefs__Skeptic__within  +   -->
<!--                 Beliefs__SpiritExcludesGod__within +  -->
<!--                 Beliefs_GodAndSpirit_within  +  -->
<!--                 Beliefs_GodExcludesSpirit_within + -->
<!--                 (1|Id), data= dfben, na.action = na.omit) -->
<!-- parameters::check_heterogeneity(mod02, group = "ID") -->
<!-- # inference holds, but can we use this method with factors? What do the contrasts mean?  -->
<!-- tab_model(mod01) -->
<!-- tab_model(mod02) -->
<!-- plot_models(mod01,mod02) -->
<!-- ``` -->

# Discussion
To be continued.

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
